Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-09-27 ms.Rnw
Saving only results of haiti 1Vaccination scenario sims

# TODO: Only save parameter values and "likelihoods".
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/lee1_end_fit.rds")) {
  lee1_end_mif <- readRDS("model1/run_level_3/lee1_end_fit.rds")
} else {
  lee1_end_mif <- bake(
    file = paste0("model1/", rl_dir, "lee1_end_fit.rds"),
    {
      foreach(
        i = 1:nrow(end_start),
        .packages = c('pomp'),
        .combine = rbind
      ) %dopar% {

@@

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/S0_sims.rds")) {
  h1_S0_sims <- readRDS("model1/run_level_3/S0_sims.rds")
} else {
  h1_S0_sims <- bake(
    file = paste0("model1/", rl_dir, "S0_sims.rds"), {

@@

      # project vacc scenario, with filtering dist, and model.
      project_from_filter2(mod = s0, PF = s0_pf, nsims = h1_scen_sims)
    },
    timing = FALSE
  )
}

# Clean-up simulations for analysis/visualization
mod1_V0_sims <- agg_mod1_sims(h1_S0_sims)
mod1_V0_probs <- get_elimProbs(h1_S0_sims, model = 1)
rm(h1_S0_sims)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/S2_sims.rds")) {
  h1_S2_sims <- readRDS("model1/run_level_3/S2_sims.rds")
} else {
  h1_S2_sims <- bake(
    file = paste0('model1/', rl_dir, 'S2_sims.rds'), {

@@

      # project vacc scenario, with filtering dist, and model.
      project_from_filter2(mod = s2, PF = s2_pf, nsims = h1_scen_NP)
    },
    timing = FALSE
  )
}

# Clean-up simulations for analysis/visualization
mod1_V1_sims <- agg_mod1_sims(h1_S2_sims)
mod1_V1_probs <- get_elimProbs(h1_S2_sims, model = 1)
rm(h1_S2_sims)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/S4_sims.rds")) {
  h1_S4_sims <- readRDS("model1/run_level_3/S4_sims.rds")
} else {
  h1_S4_sims <- bake(
    file = paste0('model1/', rl_dir, 'S4_sims.rds'), {

@@

      # project vacc scenario, with filtering dist, and model.
      project_from_filter2(mod = s4, PF = s4_pf, nsims = h1_scen_NP)
    },
    timing = FALSE
  )
}

# Clean-up simulations for analysis/visualization
mod1_V2_sims <- agg_mod1_sims(h1_S4_sims)
mod1_V2_probs <- get_elimProbs(h1_S4_sims, model = 1)
rm(h1_S4_sims)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/S3_sims.rds")) {
  h1_S3_sims <- readRDS("model1/run_level_3/S3_sims.rds")
} else {
  h1_S3_sims <- bake(
    file = paste0('model1/', rl_dir, 'S3_sims.rds'), {

@@

      # project vacc scenario, with filtering dist, and model.
      project_from_filter2(mod = s3, PF = s3_pf, nsims = h1_scen_NP)
    },
    timing = FALSE
  )
}

# Clean-up simulations for analysis/visualization
mod1_V3_sims <- agg_mod1_sims(h1_S3_sims)
mod1_V3_probs <- get_elimProbs(h1_S3_sims, model = 1)
rm(h1_S3_sims)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/S1_sims.rds")) {
  h1_S1_sims <- readRDS("model1/run_level_3/S1_sims.rds")
} else {
  h1_S1_sims <- bake(
    file = paste0('model1/', rl_dir, 'S1_sims.rds'), {

@@

      # project vacc scenario, with filtering dist, and model.
      project_from_filter2(mod = s1, PF = s1_pf, nsims = h1_scen_NP)
    },
    timing = FALSE
  )
}

# Clean-up simulations for analysis/visualization
mod1_V4_sims <- agg_mod1_sims(h1_S1_sims)
mod1_V4_probs <- get_elimProbs(h1_S1_sims, model = 1)
rm(h1_S1_sims, h1_scen_NP, h1_scen_sims)

gc()
@

<<Load Model 2 VaccScenarios, message=FALSE, include=FALSE>>=
# load('model2/output/mod2_vacc_scenarios.rda')

# Run Vaccination scenarios for Model 2. Note that the code runs the same
# speed for each run-level.
mod2_VaccScenarios <- bake(
  file = paste0("model2/", rl_dir, "VaccinationScenarios.rds"), {
    haiti2_vaccScenario(
      h2_params = h2_fit$h2_params
    )
  },
  timing = FALSE
)

>>>>

if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/lee1_end_fit.rds")) {
  lee1_end_mif <- readRDS("model1/run_level_3/lee1_end_fit.rds")
} else {
  lee1_end_mif <- bake(
    file = paste0("model1/", rl_dir, "lee1_end_fit.rds"),
    {
      foreach(
        i = 1:nrow(end_start),
        .packages = c('pomp'),
        .combine = rbind
      ) %dopar% {

@@

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/S0_sims.rds")) {
  h1_S0_results <- readRDS("model1/run_level_3/S0_sims.rds")
} else {
  h1_S0_results <- bake(
    file = paste0("model1/", rl_dir, "S0_sims.rds"), {

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S0_sims <- project_from_filter2(mod = s0, PF = s0_pf, nsims = h1_scen_sims)

      results <- list()
      results$mod1_V0_sims <- agg_mod1_sims(h1_S0_sims)
      results$mod1_V0_probs <- get_elimProbs(h1_S0_sims, model = 1)

      results
    },
    timing = FALSE
  )
}

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/S2_sims.rds")) {
  h1_S2_results <- readRDS("model1/run_level_3/S2_sims.rds")
} else {
  h1_S2_results <- bake(
    file = paste0('model1/', rl_dir, 'S2_sims.rds'), {

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S2_sims <- project_from_filter2(mod = s2, PF = s2_pf, nsims = h1_scen_NP)

      results <- list()
      results$mod1_V1_sims <- agg_mod1_sims(h1_S2_sims)
      results$mod1_V1_probs <- get_elimProbs(h1_S2_sims, model = 1)

      results
    },
    timing = FALSE
  )
}

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/S4_sims.rds")) {
  h1_S4_results <- readRDS("model1/run_level_3/S4_sims.rds")
} else {
  h1_S4_results <- bake(
    file = paste0('model1/', rl_dir, 'S4_sims.rds'), {

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S4_sims <- project_from_filter2(mod = s4, PF = s4_pf, nsims = h1_scen_NP)

      results <- list()
      results$mod1_V2_sims <- agg_mod1_sims(h1_S4_sims)
      results$mod1_V2_probs <- get_elimProbs(h1_S4_sims, model = 1)

      results
    },
    timing = FALSE
  )
}

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/S3_sims.rds")) {
  h1_S3_results <- readRDS("model1/run_level_3/S3_sims.rds")
} else {
  h1_S3_results <- bake(
    file = paste0('model1/', rl_dir, 'S3_sims.rds'), {

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S3_sims <- project_from_filter2(mod = s3, PF = s3_pf, nsims = h1_scen_NP)

      results <- list()
      results$mod1_V3_sims <- agg_mod1_sims(h1_S3_sims)
      results$mod1_V3_probs <- get_elimProbs(h1_S3_sims, model = 1)

      results
    },
    timing = FALSE
  )
}

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
if (RUN_LEVEL != 3 & file.exists("model1/run_level_3/S1_sims.rds")) {
  h1_S1_results <- readRDS("model1/run_level_3/S1_sims.rds")
} else {
  h1_S1_results <- bake(
    file = paste0('model1/', rl_dir, 'S1_sims.rds'), {

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S1_sims <- project_from_filter2(mod = s1, PF = s1_pf, nsims = h1_scen_NP)

      results <- list()
      results$mod1_V4_sims <- agg_mod1_sims(h1_S1_sims)
      results$mod1_V4_probs <- get_elimProbs(h1_S1_sims, model = 1)

      results
    },
    timing = FALSE
  )
}
@

<<Load Model 2 VaccScenarios, message=FALSE, include=FALSE>>=

# Run Vaccination scenarios for Model 2. Note that the code runs the same
# speed for each run-level.
mod2_VaccScenarios <- bake(
  file = paste0("model2/VaccinationScenarios.rds"), {
    haiti2_vaccScenario(
      h2_params = h2_fit$h2_params
    )
  },
  timing = FALSE
)
@
